---
title: "BiocHubsShiny: Interactive Display of Hub Resources"
author:
- name: Marcel Ramos
  affiliation: "CUNY Graduate School of Public Health and Health Policy, New York, NY USA"
- name: Vincent J. Carey
  affiliation: "Channing Lab, Brigham and Womens Hospital, Harvard University, Boston, MA USA"
package: BiocHubsShiny
output:
  BiocStyle::html_document:
    toc: false
vignette: >
  %\VignetteIndexEntry{BiocHubsShiny Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    cache = TRUE,
    out.width = "100%"
)
BHSimagePath <- function(name, branch = "devel") {
    if (curl::has_internet())
        glue::glue(
            "https://github.com/Bioconductor/BiocHubsShiny/blob/{branch}",
            "/vignettes/figures/{name}?raw=true"
        )
    else
        glue::glue("figures/{name}")
}
```

# BiocHubsShiny

The `BiocHubsShiny` package allows users to visually explore the `AnnotationHub`
and `ExperimentHub` resources via `shiny`. It provides a tabular display of the
available resources with the ability to filter and search through the column
fields.

# Installation

```{r,eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("BiocHubsShiny")
```

# Loading the package

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(BiocHubsShiny)
```

# Display of resources

Resources are displayed interactively using the eponymous function:

```{r,eval=FALSE}
BiocHubsShiny()
```

```{r,echo=FALSE}
knitr::include_graphics(
    BHSimagePath("BiocHubsShiny.png")
)
```

# Filtering

You can filter by any of the columns in the table. For example, you can search
for 'Mus musculus' to get resources only for that species:

```{r,echo=FALSE}
knitr::include_graphics(
    BHSimagePath("MusMusculus.png")
)
```

# Selection

Click on the rows to select the resources. They will show up as highlighted
rows.

```{r,echo=FALSE}
knitr::include_graphics(
    BHSimagePath("MusMusculusSelection.png")
)
```

# Import

Once the selection is highlighted, the code at the bottom of the app
will be updated to show the commands for entering (reproducibly) into
the R session. 

```{r,echo=FALSE}
knitr::include_graphics(
    BHSimagePath("MusMusculusCode.png")
)
```

# Session Info

```{r}
sessionInfo()
```

